LME-MPM applied to quasi-brittle fracture.

### 2020-06-30 2020_EFM_MPM_Eigensoftening.tex
Updates from Overleaf

Figure \ref{fig:Reactions-cracked-panel-mode-I} support this since it
does not exhibits it when particles cross element borders as occur
with linear interpolation. Unfortunately the extended support of this

>>>>

Figure \ref{fig:Reactions-cracked-panel-mode-I} supports this fact since it
does not exhibit instabilities when particles cross element borders meanwhile these instabilities are found with linear interpolation. Unfortunately, the extended support of this
